%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------


\documentclass{resume}

\usepackage[parfill]{parskip} % Remove paragraph indentation
\usepackage{array} % Required for boldface (\bf and \bfseries) tabular columns
\usepackage{ifthen} % Required for ifthenelse statements

\pagestyle{empty} % Suppress page numbers



\usepackage[left=0.6in,top=0.3in,right=0.6in,bottom=0.3in]{geometry} % Document margins

 \usepackage{url}

\name{Aidarbek Suleimenov} % Your name

\address{suleimenov.aidarbek@gmail.com \\ aidarbek.github.io \\ +7 777 554 85 76}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Nazarbayev University} \hfill {\em August 2016 - June 2020 (expected)} \\ 
B.S. in Computer Science.\\
{\bf Nazarbayev University} \hfill {\em September 2015 - June 2016} \\ 
Foundation program in Physics and Math \\
Got accepted into program with around 20\% acceptance rate
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
%------------------------------------------------
\begin{rSubsection}{Bloomberg L.P.}{June 2018 - August 2018}{ Software Engineering Intern}{London, UK}
\item Improved JSON encoding plugin for stock exchange parsers in \textbf{C++} with RapidJSON and template metaprogramming, made it 50\% faster and more flexible with less code for plugin users. 
\item Developed \textbf{Python} multiprocessing scripts for data migration to \textbf{Hive}.
\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{Bloomberg L.P.}{May 2017 - September 2017}{ Software Engineer, Industrial placement}{London, UK}
\item Constructed data pipeline with \textbf{Apache Spark} framework, \textbf{Oozie} workflow manager and \textbf{Python} programming language
\item Improved performance of querying  \textbf{Hive} database by 2-3 times.
\end{rSubsection}


%------------------------------------------------
%------------------------------------------------
\begin{rSubsection}{RiteTag}{June 2016 - August 2016}{Software Engineering Intern}{Remote}
\item Integrated Google Drive and Reddit \textbf{API}s into existing \textbf{PHP} product.
\item Created machine learning project for sentiment analysis of tweets using \textbf{sklearn}.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Kazakh-Turkish High School}{September 2014 - May 2015}{Teaching Assistant}{Astana, Kazakhstan}
\item Gave computer science lectures on \textbf{algorithms and data structures} in \textbf{C++} and mentored secondary school students.
\item Covered topics such as: C++ syntax, complexity of algorithms, dynamic and greedy programming, basic graph algorithms, brute force algorithms, various data structures, etc.
\end{rSubsection}

%------------------------------------------------



\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards and recognitions}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Bronze medal in international Eurasian team olympiad in informatics 2014 (top 1-2\%) \\
Bronze medal in national olympiad in informatics 2015 (top 2-3\% across Kazakhstan)\\
1st place at city olympiad in informatics 2014, 2015 (30+ participants) \\
Participated in internal Bloomberg CodeCon 2017 (top 20\%)
\end{tabular}

\end{rSection}



\begin{rSection}{Projects}

\begin{rSubsection}{Make Twitter Great Again}{\url{https://www.producthunt.com/posts/make-twitter-great-again}}{September 2016}{}
Got 300+ upvotes at the Product Hunt website and was ranked \#1 in Tech  during September 18, 2016. Collaborated with friends and used \textbf{sklearn} and \textbf{Flask} libraries for \textbf{Python}.
\end{rSubsection}

\begin{rSubsection}{Music recommendation}{\url{https://github.com/aidarbek/music_recommendation}}{June 2016}{}
Developed a service that recommends three tracks on the basis of your favourite track. Implemented it using \textbf{Ruby on Rails}. 
\end{rSubsection}

\end{rSection}

\begin{rSection}{Publications}

\begin{rSubsection}{}{}{}{}
Sterling, M., \textbf{Suleimenov, A.} (in press). Patterns of Syntax Theme Customization for Code Editors. 2018 IEEE 3rd International Conference on Communication and Information Systems.

\end{rSubsection}


\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}

